Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-05-30 paper.Rnw
Added discussion notes and removed even numbers from the A2A plots

  \item[Cross-correlation Weighted Majority Vote]
  An optimal combination of targets from the template library has previously been
  shown to improve segmentation accuracy \citep{Aljabar2009,Collins2010}.  In this
  method, each template library image is ranked in similarity to each unlabelled 
  image by the normalized cross-correlation (CC) of image intensities after linear
  registration, over a region of interest (ROI) generously encompassing the 
  hippocampus.  Only the top ranked template library image labels are used in a
  voxel-wise majority vote. The ROI is heuristically defined as the extent of all
  atlas labels after linear registration to the template, dilated by three voxels
  \citep{Chakravarty2012}.  The number of top ranked template library image labels
  is a configurable parameter.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<ADN1-xval-k-mean, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(all_data_mean, 
       aes(x=templates.mb,y=k.mb, colour=as.factor(atlases))) + 
  facet_grid(reg_method~method.mb) + 
  stat_summary(fun.y=mean,geom='line',
               aes(y=k.mb, weight=1)) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" ) + 
  opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \label{fig:ADNI1-xval-k_mean}
  \caption{
  {\bf Mean DSC of \mb segmentations across 69 ADNI1 subjects, by atlas and
  template library size, registration algorithm, and label fusion method.} 
  }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: "increase" in mean kappa over multi-atlas
\begin{figure}
<<ADN1-Xval-k-diff,cache=TRUE,dependson='ADNI1-Xval-prep',fig.width=6,fig.height=4>>=
ggplot(subset(all_data_mean, reg_method=="ANTS" & method.mb=="Majority Vote" &
                templates.mb %in% seq(1,20,2)), 
       aes(x=templates.mb, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_summary(fun.y=mean, geom="line", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,2)) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(legend=FALSE) + 
  scale_linetype_discrete(legend=FALSE) + 
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean DSC" ) +
  opts(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{The difference in mean DSC between \mb and multi-atlas segmentations for 
  a range of parameter settings.}
  \label{ADNI1-xval-k-diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

ggplot(subset(stats.tests, direction > 0), 
  aes(x=templates.mb, y=p.value, colour=as.factor(atlases))) + 
  facet_grid( . ~ stat) + 
  geom_line(size=1) +
  geom_point(size=3) + 
  geom_hline(aes(yintercept=0.05, alpha=0.5), linetype='dashed') + 
  geom_hline(aes(yintercept=0.01, alpha=0.5), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,by=2)) + 
  scale_y_log10(limits=c(0.001,1), breaks=c(0.01,0.05,0.1,1.0)) + 
  xlab( "Number of Templates" ) + 
  ylab( "p-value" ) +
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_size_continuous(guide='none') + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{{\bf Difference in variability of \mb vs. multi-atlas segmentation 
  accuracy.}
  Variability of segmentation accuracy within 10 rounds of validation per subject. 
  Standard deviation and variance is computed per subject for both \mb and 
  multi-atlas, and the distribution of these test statistics is compared with a 
  t-test. The p-value of this test, is shown on the y-axis (scaled logarithmically).
  Only points where \mb mean variability is lower multi-atlas are shown.}
  \todo{note log scale}
  \label{ADNI1-xval-variability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                                     %%%%%
%%%%%    RESULTS: Experiment 3, Application of \mb to the segmentation    %%%%%
%%%%%                       of schizophrenia patients                     %%%%%
%%%%%                                                                     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment 3 Results: Application to the segmentation first episode
\\ \mbox{schizophrenia patients}}

@@

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      #geom_text(aes(y=value,x=DX, vjust=-1.4, size=1,
      #              label=paste("r==", signif(corr, digits=3))), 
      #      colour='black',parse=TRUE, data=snt.tests) +
      xlab("Diagnosis") + 
      ylab(expression(paste("Bilateral whole hippocampal volume (", mm^3, ")")))
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

@@

ggplot(melted, aes(x= SNT, y = diff)) + 
  geom_hline(yintercept = limits, linetype=2, color='brown') + 
  annotate("text", y = limits, x=Inf, label=round(limits,1), 
            hjust=1.1,vjust=-0.8, size=3) + 
  geom_point() + 
  xlab('Mean of manual and MAGeT-Brain hippocampal volume') + 
  ylab('Difference between Manual and MAGeT-Brain hippocampal volume') + 
  geom_smooth(method="lm", formula = y~x)
@
  \caption{Bland-Altman plot comparing manual (SNT) and \mb hippocampal volumes 
  in the \adnidataset dataset.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}

\begin{figure}
<<ADN1-src-subfield, cache=TRUE, dependson='ADNI-baseline-volumes-prep', fig.width=4, fig.height=4>>=
adni_69_RIDs = c(295,413,619,685,729,782,938,954,1018,1155,907,981,222,324,448,
                 546,553,572,602,610,814,1341,675,681,731,1130,41,68,70,101,
                 249,293,316,414,698,1206,1222,1339,751,1030,3,5,10,16,22,53,
                 168,183,241,1205,328,1095,991,213,159,337,343,642,753,1109,
                 1217,29,56,1188,1293,149,382,431,1202)
mb    = read.csv("data/ADNI_baseline_volumes/ADNI1_1.5T_MAGeT_volumes.csv")

# Get subjects, and diagnoses
base = read.csv("data/ADNI_baseline_volumes/ADNI1_Screening_1.5T_11_15_2012.csv")
base = subset(base, !grepl("Scaled_2", Description)) 
base$VISCODE <- factor(base$Visit, levels = c(1,2,3,4), labels=c("bl","m03","m06","m12"))
subjects = yr1[,c("Image.Data.ID", "RID","VISCODE")]  # we only need these fields
dx = unique(adnimerge[c("DX.bl", "RID", "VISCODE")])
subjects = merge(subjects, dx)

# Now create one data.frame with all the yr1 volume 
# data we have from each datasource
subregions = merge(subjects, mb, by.x="Image.Data.ID", by.y="SourceImageID", 
                   all.x=TRUE)
subregions = subset(subregions, VISCODE == "bl" & RID %in% adni_69_RIDs)
attach(subregions)
subregions$X1 = mean(X1, X101)
subregions$X2 = mean(X2, X102)
subregions$X4 = mean(X4, X104)
subregions$X5 = mean(X5, X105)
subregions$X6 = mean(X6, X106)
detach(subregions)
subregions = subregions[,!names(subregions) %in% c("Left_Hippo","Right_Hippo",
                                                   "X101","X102","X103","X105",
                                                   "X106")]
subregions.melted = melt(subregions, measure.vars=c("X1","X2","X4","X5","X6"),
                         variable.name="Subregion", value.name="Volume")
levels(subregions.melted$Subregion) <-list("CA1"="X1", "CA2/CA3"="X5",
                                           "CA4/DG"="X4", 
                                           "SR/SL/SM"="X6",
                                           "Subiculum"="X2")
ggplot(subregions.melted, aes(x=Subregion, y=Volume)) +
  geom_boxplot()
@
  \caption{}
  \label{fig:ADNI-scr-subfields}
\end{figure}
\FloatBarrier

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               Conclusion 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

>>>>

  \item[Cross-correlation Weighted Majority Vote]
  An optimal combination of targets from the template library has previously been
  shown to improve segmentation accuracy \citep{Aljabar2009,Collins2010}.  In this
  method, each template library image is ranked in similarity to each unlabelled 
  image by the normalized cross-correlation (CC) of image intensities after linear
  registration, over a region of interest (ROI) generously encompassing the 
  hippocampus.  Only the top ranked template library image labels are used in a
  voxel-wise majority vote. The ROI is heuristically defined as the extent of all
  atlas labels after linear registration to the template, dilated by three voxels
  \citep{Chakravarty2012}.  The number of top ranked template library image labels
  is a configurable parameter and displayed as the size of the template library
  in the rest of the paper.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: mean Kappa plot by atlases, templates, reg and voting method. 
\begin{figure}
<<ADN1-xval-k-mean, cache=TRUE, dependson='ADNI1-Xval-prep'>>=
ggplot(subset(all_data_mean, (templates.mb*atlases) %% 2 == 1),
       aes(x=templates.mb,y=k.mb, colour=as.factor(atlases))) + #as.factor((atlases*templates.mb) %% 2 ))) + 
  facet_grid(reg_method~method.mb) + 
  stat_summary(fun.y=mean,geom='line',
               aes(y=k.mb, weight=1, group=as.factor(atlases))) + 
    stat_summary(fun.y=mean,geom='point',
               aes(y=k.mb, weight=1, group=as.factor(atlases))) + 
  #stat_smooth(method='lm', formula=y~log(x)) + 
  scale_colour_hue(name="Atlases") +
  xlab( "Number of Templates" ) + 
  ylab( "Mean DSC" ) + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \label{fig:ADNI1-xval-k_mean}
  \caption{
  {\bf Mean DSC of \mb segmentations across 69 ADNI1 subjects, by atlas and
  template library size, registration algorithm, and label fusion method.} 
  }
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ADNI1-XVAL: "increase" in mean kappa over multi-atlas
\begin{figure}
<<ADN1-Xval-k-diff,cache=TRUE,dependson='ADNI1-Xval-prep',fig.width=6,fig.height=4>>=
ggplot(subset(all_data_mean, reg_method=="ANTS" & 
                method.mb=="Majority Vote" & (templates.mb*atlases) %% 2 == 1), 
       aes(x=templates.mb, y=k_diff, colour=as.factor(atlases))) + 
  #facet_grid(reg_method~method.y) + 
  stat_summary(fun.data=mean_cl_boot,geom='errorbar',
               aes(y=k_diff,colour=as.factor(atlases), width=0.2)) +
  stat_summary(fun.y=mean, geom="point", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  stat_summary(fun.y=mean, geom="line", 
               aes(y=k_diff,colour=as.factor(atlases))) + 
  #stat_smooth(method=lm, formula=y~log(x)) + 
  geom_hline(aes(alpha=0.5, yintercept=0), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,2)) + scale_y_continuous(breaks=seq(-1,1,by=0.01)) + 
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide = "none") + 
  scale_linetype_discrete(guide = "none") + 
  xlab( "Number of Templates" ) + 
  ylab( "Difference in mean DSC" ) +
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{The difference in mean DSC between \mb and multi-atlas segmentations for 
  a range of parameter settings.}
  \label{ADNI1-xval-k-diff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

ggplot(subset(stats.tests, direction > 0), 
  aes(x=templates.mb, y=p.value, colour=as.factor(atlases))) + 
  facet_grid( . ~ stat) + 
  geom_line(size=1) +
  geom_point(size=3) + 
  geom_hline(aes(yintercept=0.05, alpha=0.5), linetype='dashed') + 
  geom_hline(aes(yintercept=0.01, alpha=0.5), linetype='dashed') + 
  scale_x_continuous(breaks=seq(1,20,by=2)) + 
  scale_y_log10(limits=c(0.001,1), breaks=c(0.01,0.05,0.1,1.0)) + 
  xlab( "Number of Templates" ) + 
  ylab( "p-value" ) +
  scale_colour_hue(name="Atlases") +
  scale_alpha_continuous(guide='none') + 
  scale_linetype_discrete(guide='none') + 
  scale_size_continuous(guide='none') + 
  theme(legend.direction = "horizontal", legend.position = "bottom")
@
  \caption{{\bf Difference in variability of \mb vs. multi-atlas segmentation 
  accuracy.}
  Variability of segmentation accuracy within 10 rounds of validation per subject. 
  Standard deviation and variance is computed per subject for both \mb and 
  multi-atlas, and the distribution of these test statistics is compared with a 
  t-test. The p-value of this test, is shown on the y-axis (scaled logarithmically).
  Only points where \mb mean variability is lower multi-atlas are shown.}
  \label{ADNI1-xval-variability}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\FloatBarrier
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%                                                                     %%%%%
%%%%%    RESULTS: Experiment 3, Application of \mb to the segmentation    %%%%%
%%%%%                       of schizophrenia patients                     %%%%%
%%%%%                                                                     %%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Experiment 3 Results: Application to the segmentation of first episode
\\ \mbox{schizophrenia patients}}

@@

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/FEP-montage.pdf}
  \end{centering}
  \caption{Sagittal slices from two subjects showing a comparison of the
  original Winterburn atlas subfield segmentations (at 0.3mm3-isotropic voxel
  resolution), the downsampled Winterburn segmentations (at 0.9mm3-isotropic
  voxel resolution), and the MAGeT brain labels on the downsampled atlas image.}
  \label{fig:FEP-montage}
\end{figure}

@@

\begin{figure}[h]
<<ADNI-scr-volumes-boxplot,dependson='ADNI-baseline-volumes-prep',cache=T,fig.width=6,fig.height=4>>=
melted = melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT"),
              variable.name="Method", value.name="Volume")
correlations = ddply(melted, c("DX","Method"), function (df) {
  data.frame(
    pearson = cor(df$SNT, df$Volume)
  )
})

qplot(DX,value,data=melt(totals.complete,measure.vars=c("FS", "FSL", "MAPER","MAGeT","SNT")),
      colour=variable,geom="boxplot") + 
      #geom_text(aes(y=Inf,x=interaction(DX,Method), vjust=2, label=pearson, colour=Method), size=3, data=correlations) +
      xlab("Diagnosis") + 
      ylab(expression(paste("Bilateral whole hippocampal volume (", mm^3, ")")))
@
  \caption{Comparison of hippocampus volumes obtained by FreeSurfer (FS), FSL, 
  MAPER, \mb (MAGeT) and manual (SNT).}
  \label{fig:ADNI-scr-volumes-boxplot}
\end{figure}

@@

ggplot(melted, aes(x= SNT, y = diff)) + 
  facet_grid( DX ~ . ) + 
  geom_hline(yintercept = limits, linetype=2, color='brown') + 
  annotate("text", y = limits, x=Inf, label=round(limits,1), 
            hjust=1.1,vjust=-0.8, size=3) + 
  geom_point() + 
  xlab('Mean of manual and MAGeT-Brain hippocampal volume') + 
  ylab('Difference between Manual and MAGeT-Brain hippocampal volume') + 
  geom_smooth(method="lm", formula = y~x)
@
  \caption{Bland-Altman plot comparing manual (SNT) and \mb hippocampal volumes 
  in the \adnidataset dataset.}
  \label{fig:ADNI-scr-Bland-Altman}
\end{figure}

\begin{figure}
  \begin{centering}
    \includegraphics[width=6in]{figure/ADNI1_SNT_MB_montage/montage.pdf}
  \end{centering}
  \caption{Manual and MAGeT segmentation results for 30 ADNI1 subjects (10
  subjects randomly selected from each disease category in the subject pool used
  in Experiment 1). Sagittal slices are shown for subject unlabelled T1-weighted
  anatomical image, SNT manual label (green), and \mb label (blue). Noted are
  examples of common segmentation idiosyncracies: 
  {\em (a)} over-estimation of hippocampal head and  
  {\em (b)} translated manual segmentation by SNT; 
  {\em (c)} under-estimation of hippocampal body and
  {\em (d)} improper inclusion of the vestigial hippocampal sulcus by \mb.}
  \label{fig:ADNI-scr-subfields}
\end{figure}

@@

\begin{verbatim}

Experiment 1: 
- address the absence of weighted-voting effects. 
  - hypothesis: the benefits of weighted voting only outweigh the resampling
    error effects when choosing from a large library.  In this experiment, the 
    template library (during weighted voting) consists of only 20 templates, so
    the most we could hope for is a "squashing" upwards of the curve towards 
    the 20-template limit (which is the same across all cases in this experiment).
  - we do see a slight "squashing" effect, with XCORR more strongly than NMI. 
    Perhaps in future experiments with larger template libraries, this could be
    explored further.
- Why don't we use STAPLE? What would we expect from STAPLE or other fusion methods? 
  - couldn't get STAPLE to work with our image formats
  - Idea: expect smoothness across range of templates (no even # dips, below)
  - perhaps more sophisticated fusion methods would boost results over majority 
    vote based techniques.

- why does MAGeT brain show a dip in average Kappa when using an even number
  templates. Does MA show this same pattern? (yes)
  - Hypothesis: our voting method is biased when breaking ties to choose the 
    label with the lowest numeric value.
  - If we compute the total number of labels fused (atlases * templates) then 
    both MB/MA perform worse when fusing an even number of labels.

- we only show a +0.02 increase in mean Kappa over multi-atlas, and this is when
  using 1 atlas (which we know from Figure 2, is when we perform worst). Why does
  this increase justify the extra effort involved in MB? 
  - decrease in variability
  - we are comparing "true" averages (see above)... does this make our criteria 
    for a worthy improvement less strict?

- how does MAGeT stack up, Kappa-wise, to other methods, in an absolute sense.
- because of the extensive cross-validation in experiment 1, we are very likely
  showing results that approach the true average of MB and MA on that dataset
  (i.e. our mid 0.8 range result is a mean across 69 subjects and 10 repetitions
  each).
- even with this caveat, do we think we do well enough?  i.e. other than parameter 
  tuning, to what extent does this experiment tell us about how MB would do in 
  practice.

- effects we are seeing is not only averaging effects (Chakravarty et al. 2012).

- take aways: as in other studies (Aljabar, Heckemann) we find that performance
  scales with the number of inputs (approx. log(n)), and that a large enough
  template library can boost performance with a small number of atlases. The use 
  of templates /can/ have a negative impact on performance (Figure 2), that is 
  balanced by the improvement of growing the template library.  Likely the negative
  impact on peformance is as a result of resampling/mislabelling error. In other 
  words, tuning MAGeT brain involves balancing the tension between an improvement 
  in peformance due to increase neuroanatomical capture and decreased peformance
  due to resampling error.

Experiment 2: 
- describe resampling error during downsampling (essentially partial volume effect 
  due to averaging/majority vote in nearest neighbour selection)
- Why would some structures have greater downsampling error than others? (i.e. what
  is it about a structure that would make it especially prone to resampling error)
  - since error is discretised to whole voxels, smaller regions will show larger
    percent error
  - average unilateral volume (approx; mm3): 
     region   volume   downsampling error
     CA1      800            2%
     CA4/DG   600          -30%
     SR/SL/SM 700           30%
     Sibculum 350            0%
     CA2/3    200           15%

- observation: when downsampling error is small (<10 percent), MB error is larger, 
  and vice versa when downsampling error is large.  Could this a case where the 
  inevitable MAGeT resampling error outweighs the small downsampling error?
- observation: MAGeT produces similar volumes for the downsampled and BRAVO images
  which demonstrates reliability. Additionally, MB's error is in the same *direction*
  as the downsampling error except for SR/SL/SM
- for MB to show less error than resampling means that voting across templates is 
  in aggregate performing better than local nearest neighbour fitting. presumably 
  we'd see the same improvement with basic multiatlas as well.

- take away: MB produces subregion volumes that are comparable or better than
  resampling error, except for the CA2/3 where error is near 25 percent (but 
  even then resampling error is ~15%)

Experiment 3: 
- what is an "acceptable" r^2 value? 
- take away: MB has proven to be robust with atlases derived from three different
  segmentation protocols (SNT, Winterburn, and now Pruessner) on three different
  populations (older with AD progression; young and healthy; young and SZ).

Experiment 4: 
- address the smaller difference in mean volume across disease classes. smaller 
  than every other method.

- address the segmentation bias towards over-estimating smaller hippocampi, and 
  underestimating larger HC

- visual inspection/QC reveals MB segmentations are satisfactory (failure rate 
  is lower than the other methods (but we may be biased. :-).

- take away: MB, with the Winterburn atlases, produces HC volumes more inline with
  SNT than FSL/FS.  Comparable to MAPER but with far fewer atlases required.

\end{verbatim}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                               Conclusion 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
